---
title: Features
---

# Features of iNZight

At its heart, iNZight is a data visualisation and exploration tool for those users with little to no prior experience with data science or statistics, and who lack the programming demands of more mainstream tools such as Python @citep:python; and R @citep:rcore;. Therefore, many of the main features relate to exploring data through visualisation, with some data manipulation techniques built in, including specification of survey designs which are automatically incoporated into the rest of iNZight. Since many users will likely want to move on to coding, and since iNZight is built with R, we provide the code history for actions the user makes.



## Data wrangling

The first thing most users will want to do is import their data. iNZight provides an easy to use *Import Data* window which uses the file extension to detect the file type and provide a preview of the data in the same window. This allows users to quickly see if everything is OK and, if necessary, adjust some of the type-specific options to get it correct. An example of this might be reading european CSV files, which use a semi-colon delimiter instead of a comma.


Once loaded, iNZight provides several important data operations, allowing users to reshape, filter, and otherwise transform their dataset. Many of these 'workflows' are taken from "R for Data Science" @citep:Wickham_2017;. These basic dataset operations are implemented using packages from the 'tidyverse' @citep:tidyverse;. For each, the @gls:gui; provides an interface with inputs corresponding to various arguments, generating an R code call which is evaluated and stored in the script. In some cases, a preview of the resulting dataset is provided, making it easier for users to investigate the result of different options. @Cref:fig:data_reshape; shows the reshape data window, allowing users to convert from wide format to long format, which is more useful for plotting.

**NOTE: find a better example of reshaping**
\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{figure/data_reshape.png}
\caption{Reshaping data is a confusing task for beginners, so iNZight's reshape window provides a simple breakdown of the steps, and importantly provides a preview of what the data will look like once reshaped.}\label{fig:data_reshape}
\end{figure}

As well as the dataset operations are *variable manipulations*, allowing users to modify individual variables in the data. For example, simple transformations (log, square-root) to renaming or reordering levels of a categorical variable, each has its own interface window that interfaces with 'tidyverse' code to perform the operations. And, if the operation you want is not available, you can specify a custom command to create a new variable.

The goal of these features is to allow users to import a range of data sets in a range of formats and convert them into a form useful for plotting---that is, *tidy format* @citep:Wickham_2017;, where each row contains a single set of observations about an individual.


## Graphics and simple data analyses

The foremost tool in iNZight's inventory is graphics, which are chosen automatically based on the users's chosen variables. For example, a numeric variable is displayed to the user as a dot plot or, if there are more than 5000~observations, a histogram, without the user needing to choose this first. A factor (refered to within iNZight as *categorical*) shows as a bar graph. This means the user focusses on exploring the data without the need to first *understand* the data.

In many other data analysis programs, graphs are created by the user first selecting the *type* of graph to display, and then choosing the variable. In an explorative sense, this makes little sense, as for example a variable called "age" might be numeric *or* categorical (for example age groups). The basic types of graphs available in 'iNZight' are shown in @cref:tab:inzplottypes;. @Cref:tab:inzplotlarge; shows "large sample" alternatives which are used when sample sizes exceed `r iNZightPlots::inzpar()$large.sample.size - 1L`. The three basic plot types are *bar charts* for exploring categorical variables, *dot plots* for exploring a single numeric variable (and possibly its relationship with another categorical variable), and *scatter plots* for exploring the relationships between two numeric variables. *Histograms* are are more useful way of exploring the distribution of values a numeric variable takes when the sample size is large (that is, seeing individual points is no longer useful, nor aesthetically pleasing), while *hexagonally binned plots* are used to replace scatter plots in the same situation, allowing users to see where the bulk of points are located. Of course, this is not the only way to look at large data, which I will get to shortly.

```{r inzplottypes,echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
library(iNZightPlots)
data(census.at.school.500, package = "iNZight")
if (!dir.exists("figure")) dir.create("figure")

d <- 4
pdf("figure/pdot.pdf", height = d, width = d, onefile = FALSE)
inzplot(~height, data = census.at.school.500)
capture.output(dev.off()) -> x

pdf("figure/pdotc.pdf", height = d, width = d, onefile = FALSE)
inzplot(height ~ gender, data = census.at.school.500)
capture.output(dev.off()) -> x

pdf("figure/pscatter.pdf", height = d, width = d, onefile = FALSE)
inzplot(height ~ armspan, data = census.at.school.500)
capture.output(dev.off()) -> x

pdf("figure/pbar.pdf", height = d, width = d, onefile = FALSE)
inzplot(~travel, data = census.at.school.500)
capture.output(dev.off()) -> x

pdf("figure/pbar2.pdf", height = d, width = d, onefile = FALSE)
inzplot(travel~gender, data = census.at.school.500, hide.legend = TRUE)
capture.output(dev.off()) -> x

# plot_types <- rbind(
#     c("Numeric", "", "dot plot", "histogram"),
#     c("Numeric", "Categorical", "dot plot", "histogram"),
#     c("Numeric", "Numeric", "scatter plot", "hexbin plot"),
#     c("Categorcal", "", "bar graph", "bar graph"),
#     c("Categorical", "Categorical", "bar graph", "two-way bar graph"),
#     c("Categorical", "Numeric", "dot plot", "histogram")
# )
# colnames(plot_types) <- c("Variable 1", "Variable 2", "Default plot", "Large-sample plot")
fig <- function(...)
    sapply(list(...),
        function(z)
            sprintf("\\includegraphics[width=0.25\\textwidth,valign=T]{figure/p%s.pdf}", z)
    )

plot_types <- data.frame(
    "Variable 1" = c("Categorical", "Numeric"),
    "None" = fig("bar", "dot"),
    "Categorical" = fig("bar2", "dotc"),
    "Numeric" = fig("dotc", "scatter")
)
library(kableExtra)
names(plot_types)[1] <- " "
knitr::kable(plot_types, "latex",
    booktabs = TRUE,
    caption = 'iNZight default plot types are determined by the variable type of the first variable and, if specified, the type of the second variable.',
    label = 'inzplottypes',
    escape = FALSE) %>%
    add_header_above(c("Variable 1", "Variable 2" = 3L)) %>%
    kable_styling(font_size = 8)
```

```{r inzplotlarge,echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
pdf("figure/phist.pdf", height = d, width = d, onefile = FALSE)
inzplot(~height, data = census.at.school.500, largesample = TRUE,
    cex.dot = 5)
capture.output(dev.off()) -> x

pdf("figure/phex.pdf", height = d, width = d, onefile = FALSE)
inzplot(height ~ armspan, data = census.at.school.500, largesample = TRUE,
    hex.bins = 10)
capture.output(dev.off()) -> x

plot_large <- data.frame(
    Plot = c("dot plot", "scatter plot"),
    Small = fig("dot", "scatter"),
    Large = fig("hist", "hex")
)
knitr::kable(plot_large, "latex",
    booktabs = TRUE,
    caption = 'iNZight\'s alternative plots for large samples. Other plot types do not have a large sample alternative (i.e., bar charts).',
    label = 'inzplotlarge',
    escape = FALSE)
```

Another way of exploring relationships is by *subsetting* or *faceting*, which is easily accessed and indeed encouraged from the iNZight interface. The two subsetting variable slots allow users to subset the plot, which presents a slider to look at individual levels of the chosen variable, as shown in @cref:fig:subsetslider;. This is particularly advantageous to exploring trends *over time*, as users can use the "Play" button and watch as iNZight automatically plays over the range of levels (which might be "years" in a longitudinal dataset). This use of motion to explore trends in the data over time was most famously demonstated by @citet:Rosling_2010; in his BBC documentary "The Joy of Stats". However, time is not the only useful subsetting variable: many other categorical variables are often important when exploring relationships in a dataset, for example age and ethnicity.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figure/subsetslider.png}
\caption{The control panel's grouping variable slots display a slider, allowing users to easily navigate between plots of various subset.}
\label{fig:subsetslider}
\end{figure}

Of course, there is only so much one can learn from subsetting, and often more advanced visualisation techniques are required. For this, iNZight provides the *Add to Plot* system, which displays a list of options for the user to adjust, and most importantly only those related to the current plot. The most notable feature is *colour*, which can either be set to a single colour or, more usefully, coded to another variable in the dataset. This panel is also reactive, so a user's choices will open up some new options (or remove others), allowing them to explore the possibilities offered without having problems (for example trying to colour a bar chart by a numeric variable). Other codable features include *point size* and *point shape* (useful for printed media or for colourblind audiences).

Other options under the *Add to Plot* system include adjusting axes (by adding transformations or changing labels), adding additional information to specific plots (trend lines and smoothers to scatter plots, for example), and *locating points*. The last of these is an essential part of data exploration: often we want to explore outliers or else identify a specific point in the data. iNZight allows users to use a *point-and-click* identification method to highlight and label specific points, which are retained in future plots (so an individual can be tracked over different variables to explore them in detail), or points can be identified contextually, either by their specific value, or as an "extreme" value.

Since switching variables often results in a change of plot, iNZight remembers most settings (for example *colour*) so those variables remain visible in the dataset. This makes it easy to explore, for example, the effect of ethnicity on other variable relationships. Since some plots do not handle all arguments, iNZight only uses those that do: for example, switching to a two-way bar plot, the "colour" variable would be ignored without being forgotten; changing back to, say, a scatter plot reactivates the colour variable.


Visually assessing relationships in the dataset is generally the first step in a more in-depth analysis, and often we find that what we thought was an effect is actually not significant. iNZight provides some simple *visual inferencial markup*
to plots that provide a visual way of exploring if a particular relationship might actually be there, or is simply a function of randomness. For example, a bar chart often hides the underlying population size, so the significance of differences in bar height is not obvious. By adding error bars, however, we can begin to make inferential calls about those differences. Another example is the trend line on a scatter plot: the sample estimate might display an upwards trend, but this may be affected by just a few points. By adding a sample of *bootstrap trend curves*, as shown in @cref:fig:scatter_bs_trend;, we can assess how *real* this relationship might be.

```{r scatter_bs_trend,echo=FALSE,fig.height=5,fig.width=6,out.width="0.8\\textwidth",fig.cap="A scatter plot with a linear trend, showing a bootstrap sample of trend curves.",fig.align="center"}
inzplot(armspan ~ height, data = census.at.school.500, trend = "linear", bs.inference = TRUE)
```

Another type of *visual inference* iNZight offers is *comparison intervals*, estimated using the 'iNZightMR' package @citep:iNZightMR;. These intervals provide adjusted intervals designed primarily for visual comparison. In the two-way bar chart shown in @cref:fig:barchart_comp;, the *within group* comparison intervals can be interpreted as "if the intervals do not overlap, then for a particular level of 'travel' there may be a different between the proportions for each 'gender'"; in the figure, the appears to be a difference between the proportion of males and females who travel by bike, but otherwise the distribution of travel is the same. It is important to note that these *are not* confidence intervals: they account for multiple comparisons and the covariance between variables.

```{r barchart_comp,echo=FALSE,fig.height=5,fig.width=6,out.width="0.8\\textwidth",fig.cap="A two-way bar chart with comparison intervals.",fig.align="center"}
inzplot(travel ~ gender, data = census.at.school.500, inference.type = "comp")
```

Having done as must visual exploration as iNZight provides, it is likely that some numerical information might be desired. For example, when discussing the data it is useful to have summary statistics, such as the mean or quantiles. iNZight provides a "Get Summary" button, which provides a simple summary of the currently displayed graph. Like the plots, the types of summaries depends on the chosen variable(s) and, in some cases, additional features (scatter plots provide extra information about the basic relationship of any fitted trend lines, for example). The primary use is to extract values from the graph, with a few extra variables (such as variance) which are considered simple summaries. The philosophy remains "look first". A simple summary of a dotplot is given in @cref:fig:dot_summary;.

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figure/dot_summary.png}
\caption{The ``Get Summary'' window for a numeric variable (`height').}\label{fig:dot_summary}
\end{figure}

Once visual and numeric exploration has been complete, the next step is often to pose and test hypotheses. Again, iNZight provides this functionality through the simple "Get Inference" button, and works similarly to "Get Summary", but with a few slight differences. The type of inference information and hypothesis tests available depend on the chosen variables, though users are also presented with some controls to specify information about their hypothesis. Additionally, *bootstrap inference* is provided which uses bootstrap sampling using the 'boot' package @citep:boot; to obtain inferences. The basic inferences include confidence intervals for most parameters, as well as $p$-values of differences (in a two-way table of counts, for example).

The choices of hypothesis test depend also on the variable types. For a sole numeric variable, a one-sample *t*-test is available in which the hypothesis value can be specified, and either a one- or two-sided test carried out. \Cref{tab:hypothesis-tests} shows the types of hypothesis tests available from iNZight.

```{r hypothesis-tests,echo=FALSE,results='asis',message=FALSE,warning=FALSE}
tab <- cbind(
    c('numeric', 'categorical', ''),
    c('', '2 levels', '2+ levels'),
    c('t-test$^1$', 'single proportion', '$\\chi^2$-test$^2$'),
    c('--', 't-test$^3$', 'ANOVA'),
    c('t-test$^3$', '$\\chi^2$-test$^{4,5}$', '$\\chi^2$-test$^4$'),
    c('ANOVA', '$\\chi^2$-test$^{4,5}$', '$\\chi^2$-test$^4$')
)
kable(tab,
    "latex",
    booktabs = TRUE,
    caption = 'iNZight hypothesis test options. ',
    label = 'hypothesis-tests',
    # align = "center",
    escape = FALSE) %>%
    add_header_above(c('', '', 'NULL', 'numeric', '2 level cat', '2+ level cat')) %>%
    add_header_above(c("Variable 1" = 2L, "Variable 2" = 4L)) %>%
    add_footnote(
        c(
            'One-sample',
            'Equal proportions',
            'Two-sample',
            'Equal distributions',
            'Additionally includes epidemiological output such as odds and risk ratios.'
        ),
        'number', threeparttable = TRUE) %>%
    kable_styling(font_size = 8)
```

This concludes the main functionality of iNZight for beginners: the ablity to load a data set and instantly view graphs and summary information, and perform hypothesis tests without having to understand how these fit together. iNZight provides a platform with with learners can explore on their own, and learn as they go.


## Saving code history

As a statistics and data science learning tool, iNZight not only provides a way to learn data explorationg and visualisation, but also has begun a process of teaching basic coding through provision of R code scripts and snippets. All of iNZight's functionality is driven by calls to R functions, for which we can save the code for users to view later. This provides two things: first, a 'transcript' of a user's session, which is an essential part of *reproducible research* and allows sharing of their results; second it provides them with a script they can copy, paste, and edit to run in their own R session.

The code history script is a simple method of providing code, but it lacks *interactivity*. However, the latest version of iNZight (4.0.0) introduces a (developmental) "code widget" which gives the R code for the current plot. This has a bi-directional link with the @gls:gui;: when the user changes settings in the @gls:gui;, the code updates to reflect the change; but also if the user chooses to modify the *code* and run it, then the @gls:gui; controls are updated. This allows users to get a feel for writing code and setting how it affects the result.


### Saving an R script

All of iNZight's methods call functions in other packages, many of which are themselves 'wrapper' functions. As an example, the Filter Data window in iNZight calls to the `filterData()` function in the 'iNZightTools' package @citep:iNZightTools;, which returns the 'tidyverse' @citep:tidyverse; code used to perform the filtering steps. The code is extracted as follows:
\begin{lstlisting}[language=R]
library(iNZightTools)
data.filtered <- filterLevels(iris,
    var = "Species",
    levels = "Setosa")
cat(code(data.filtered))
# iris %>% dplyr::filter(Species == "Setosa")
\end{lstlisting}

The iNZight @gls:gui; simply fetches the code attached to each command it calls and appends it to the R history script. One main advantage of this, particularly using wrapper functions, is that the @gls:gui; does not need to know anything about the code---only that it exists. Therefore, improvements or changes could be made to the wrapper function, and these would be reflected in the resulting script without any changes to the @gls:gui;.


### Live code editing

A more complex relationship exists between the 'code panel' widget, visible by turning on developmental features from the preferences menu. This module is displayed at the bottom of the window, as shown in @cref:fig:code_panel;. Changing the configuration from the variables or the Add to Plot panel will update the code automatically, and vice verca.

\begin{figure}
\centering \includegraphics[width=\textwidth]{figure/code_panel.png}
\caption{The code panel shown at the bottom of the iNZight window describes all of the user's chosen settings for the current graph.}
\label{fig:code_panel}
\end{figure}

To make this work, iNZight stores all of its settings in a single `list()`, in which each item corresponds to an argument passed to the `inzplot()` function (in the 'iNZightPlots' package @citep:iNZightPlots;). From the `defaults()` function, we can obtain the list of 'default' values, and remove those settings that the user has not changed. These are then parsed together to construct the code call.

The reverse involves a little more work, since the code call needs to be converted into a `list()` object first. Then, it is compared to the current list and any changes are converted into actions in the interface. For example, if the user changes the value of `g1.level` in @cref:fig:code_panel;, the value of the slider will be adjusted accordingly after comparing the change to the settings list.

The limitation of this approach is that it only works for the `inzplot()` function, and only accepts arguments the @gls:gui; has been coded to handle (any extra arguments are simply ignored). However, it does provide a very simple, elegant interface for users already familiar with 'iNZight' to begin exploring how code works.


## Analysing surveys with iNZight

Survey data is common in official statistics, and has been fully integrated into 'iNZight' to allow researchers to explore data from surveys with as much ease as they would standard data. To do so, 'iNZight' requires the survey information to be specified once, at which point all future actions will be performed using the survey design. This includes graphics, summaries and inference, data manipulation, and code writing. The most common survey structures are supported: stratified and cluster based surveys, replicate weights, as well as post-stratification or calibration of surveys using additional data.


There are three ways of specifying survey information to 'iNZight'. The first uses a simple dialog window asking the user to input the information manually, as shown in @cref:fig:survey_spec;. This allows users to specify the design of a survey if they already know it, and provides a straightforward interface to do so. However, it does make it difficult for learners and researchers not as familiar with the design to get started with their exploration. To get around this, we added two new methods for specifying survey information from a separate file.

\begin{figure}
\centering \includegraphics[width=0.6\textwidth]{figure/survey_spec.png}
\caption{Specifying survey information in the survey specification window.}
\label{fig:survey_spec}
\end{figure}

The first of the two methods again uses the survey specification window, but allows users to locate a pre-configured file containing the survey design information in a specific format. 'iNZight' reads this file and applies the information to the existing dataset. The last method makes it even simpler, and only requires users to import one single file: the survey design specification (so long as the data is in the same directory). This is imported through 'iNZight's standard "Import Data" interface, and automatically loads the data and sets up the design all in one single step.

some stuff about the format of the survey spec file.


Having specified survey design information, users will, in most situations, not have to worry about any other changes to their iNZight workflow. Graphs will automatically take into account the survey information, summaries and inferences will too. Even data manipulation switches over to survey-counterparts, and the code written to the R script remains valid.


Behind the scenes, iNZight passes around a survey object, which external helper functions (in the 'iNZightTools' package, for example) can expect. Many of the manipulation methods use functionality from the 'srvyr' package @citep:srvyr; to provide 'dplyr'-like syntax @citep:dplyr;, and minimises special handling of survey data. In cases where the syntax is not possible, we simply use `update()` to add, manipulate, or remove variables within the survey design.

When iNZight recieves a new survey design object, it extracts the data and displays this to the user. In this way, iNZight can natively pass survey objects around any displays the information accordingly.



## Other modules

The main iNZight window focusses on simple exploration and analysis of a standard dataset. However, there are many situations where a dataset may have unique features (such as time series or map data) or a user might want to perform some more complex operations (model fitting, for example). Rather than attempting to integrate these into the main iNZight program---which would quickly become unwieldy---we created individual *modules*, accessible from the **Advanced** menu. Here, we overview the structure of these modules, and demonstrate a few of them.


### The structure of iNZight's modules

Similarly to the components discussed in \cref{an-overview-of-inzights-structure}, each of the modules is itself a Reference Class object, contained within the 'iNZightModules' packages @citep:iNZightModules;. These modules are able to call a helper function of the main GUI object, allowing them to replace the left-hand-side control panel.

Each module is designed with a singular data type or statistical method in mind. For example, the *Time Series* module requires time-based data, and provides functionality to draw, decompose, and forecast time series data. Being a *child* of the main GUI, these modules have access to the dataset imported by the user, as well as the ability to change the menu items and plot toolbar to add custom buttons.

Module layout is typically constructed in the same way an analysis script might be, from top to bottom. The user starts out be choosing variables of interest, or providing necessary information (such as a time variable) to the module. Then, new options are activated, logically stepping the user through the process of exploring their data. In some, such a the Model Fitting module, various sections of the interface are containing within expandable frames to keep the interface uncluttered. However, firmly at the center of all the modules, is *graphics*: a plot is displayed as soon as possible, and updated as the user changes various inputs.

Within each module, there are usually one or two calls to external 'wrapper functions', either other packages maintained by the 'iNZight' team (for example, the Time Series module calls functions in the 'iNZightTS' package), or elsewhere. These packages are, however, also designed to be standalone packages, once again in an attempt to bridge the gap between high- and low-level code. These packages provide simple wrappers for some complex actions, which are user-visible and may, in time, be accessible through the interface (similarly to the plot code in the main iNZight interface).


### Built-in modules

iNZight is shipped with several advanced modules, detailed below. These provide visualisation and analysis functionality for some common data types and processes(?). Here we give a quick overview of the functionality provided by each.


#### Time Series

A common type of data available, and of interested, to users is time series data, so of course iNZight provides a module dedicated to visualising these types of data. When loaded, the module attempts to detect a 'time' variable, and otherwise asks the user to provide one. Alternatively, users may manually provide time information, for example if the information is not available or formatted incorrectly. Once done, iNZight displays a graph of the first variable in the dataset over time, as shown using the "Quarterly New Zealand visitors" data in @cref:fig:ts_visitors;.

\begin{figure}
\centering \includegraphics[width=\textwidth]{figure/ts_visitors.png}
\caption{Visitors data.}
\label{fig:ts_visitors}
\end{figure}

Users can choose between multiplicative (the default) and additive models, and have prominent control over the 'smoothness' of the trend line. This allows users to see how results can change based on the level of smoothing. The available variables are presented, and can either be displayed one-at-a-time, or multiple-selected to compare series. The @gls:stl; algorithm @citep:Cleveland_1990; is used to provide the decomposition and seasonal graphs, and Holt-Winters' algorithm @citep:Holt_2004,Winters_1960; is used for forecasting.



#### Multiple Response

A seldom discussed data type is *multiple response*, which typically come from surveys with 'tick all that apply' type answers. The 'iNZightMR' package @citep:iNZightMR; provides methods for analysing these types of data, such as calculating the proportion of responses in each category with the correct standard errors. The *Multiple Response* module connects to the aforementioned package, and when loaded presents the user with a list of 'binary' variables in the dataset (that is, with a 0/1 or 'yes'/'no' value). These can be multiple-selected and a graph is displayed.

In the example of @cref:fig:mr_tech;, the responses of students to a questionnaire about what technologies they have used is shown, subset by age and gender. The error bars account for multiple responses, and the horizontal yellow lines are 'comparison intervals', which indicate a difference between groups if they do not overlap. Another graph available is the "Combinations" plot, showing the frequency of various combinations of responses (@cref:fig:mr_comb;). This allows users to explore the frequency of response combinations.


\begin{figure}
\centering \includegraphics[width=\textwidth]{figure/mr_tech.png}
\caption{Student responses to having using various technologies.}
\label{fig:mr_tech}
\end{figure}
\begin{figure}
\centering \includegraphics[width=\textwidth]{figure/mr_comb.png}
\caption{Combinations of responses as to having used various technologies.}
\label{fig:mr_comb}
\end{figure}


#### Maps

A hugely popular type of data is geographical data in a huge variety of forms. iNZight's Map module allows users to plot location data (i..e, longitude/latitude coordinates on a map) or regional data (countries, regions, etc). For point-type data, these are effectively a scatter plot with a map underneath, and include much of the same functionality: subsetting, colour, resizing, and so on. Regions are different, however, in that they require *shape files*, which describe the boundaries of various regions. For example, the world shape file includes shapes of countries.

The difficulty with shape data is merging the shapes to the original data, since some countries are commonly spelled differenctly or using a range of different country codes. The iNZight Maps module automatically tries to guess the best match, and allows users to override this to improve matches, or manually match unmatched countries. It also lets users choose between a variety of shape files, including world maps, region maps (europe, america, etc), and some other specialised maps (for example New Zealand electoral districts). User may also import their own shapefile, if desired.

Once imported, variables can be chosen to graph on the map, in which case regions are coloured by the variable. Categorical variables are given one colour per category, while numeric are given a continuous colour palette and coloured accordingly. Additionally, a *time* variable can be included, in which case summaries can be graphed (e.g., mean, median, maximum, etc) or a mini time series "spark line" graph can be drawn on each region. This is demonstrated in @cref:fig:map_spark;.

\begin{figure}
\centering \includegraphics[width=\textwidth]{figure/map_spark.png}
\caption{Sparklines on a map.}
\label{fig:map_spark}
\end{figure}


#### Model Fitting

The final module built in to iNZight provides arguably the most used methods of statistics: regression modelling. This module provides normal, binomial, and Poisson modelling of a single response variable, and users may add variables as predictors either by drag-and-drop or double-cliking. The residual plot and summary output are updated instantly, allowing users to build up a model interactively. Additional summary plots are available, such as Cooks' distance, QQ-plots, and histograms. iNZight Model Fitting uses graphs provided by the 'iNZightRegression' package @citep:iNZightRegression;. A novel contribution is the display of bootstrap smoothers on graphs, as well as *bootstrap QQ-plots* and a *boostrap array of histograms*, allowing users to visually compare what the residual distribution might look like (i.e., under small sample sizes, non-normality might be due to chance). Another feature of the Model Fitting module is saving and later comparing (either via AIC or BIC) alternative models.


### Addon modules

Updating modules within a package is a drawn-out process, and requires the package maintainer to sort out updates and release. To this, we recently began trialing a new "Add-on" system, allowing individual modules (each a single R file containing a reference class object) to be added, updated, and removed as needed. In this way, individuals---be it members of the 'iNZight' team, teachers of various statistics courses, or researchers---can develop their own modules and install these into iNZight. By using Github pull requests, they may have their work integrated into the 'official' iNZight addon repository, or they can distribute a file to their users who can install the module from a local file. This kind of structure is seen in many other programs, for example Excel and Notepad++ @citep:cn;.

One exciting new addon being developed is the 'Bayesian demographic modelling' module, which connects to a set of packages used to perform the type of analysis used by @cite:Zhang_2019;. This work will provide small communities, demographics, and nations to explore and analyse their own data using a tool with which they are either already familiar, or has a very easy learning curve: iNZight.
